### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, and all four $fc$ in \bfc are updated from $fc$ (1, 1) to $fc_{\Delta}$ (1, 0), as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
% 
\identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx,
	since $tc (1, 1) \& fc_{\Delta}(1, 1) = fc_{\Delta}(1, 1)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.
Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.

>>>>

\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, and all four $fc$ in \bfc are updated from $fc$ (1, 1) to $fc_{\Delta}$ (1, 0), as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
% 
\identifyaffball firstly identifies ball $\ball{[\kw{PM_1},2]}$ with $tc$ $(1, 1)$ and $\ball{[\kw{PM_2},2]}$ with $tc$ $(1, 0)$ as \affballsx,
	since $tc (1, 1) \& fc_{\Delta}(1, 0) = fc_{\Delta}(1, 0)$ and $tc (1, 0) \& fc_{\Delta} (1, 0) = fc_{\Delta}(1, 0)$.
Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.
